---
title: "Getting Started"
author: "Eric Tchong"
date: "2019-06-04"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

First, load the **Rinstapkg** package and log in. There are two ways to authenticate:  

  1. OAuth 2.0
  2. Basic Username-Password

It is recommended to use OAuth 2.0 if you apply for and are approved for an Instagram App. 
This way multiple users can use your app without having to explicity share their 
credentials with you. Note that the OAuth credentials will be stored in locally 
cached file entitled ".httr-oauth-Rinstapkg" in the current working directory.  

If you do not have an approved app, you can still use this package by providing your 
username and password.

```{r auth, include=FALSE, message=FALSE, warning=FALSE}
library(Rinstapkg)

# OAuth2.0 token authentication, which we won't use here
#token_path <- here::here("tests", "testthat", "Rinstapkg_token.rds")
#suppressMessages(ig_auth(token = token_path, verbose = FALSE))

# Username-Password authentication
settings <- readRDS(here::here("tests", "testthat", "Rinstapkg_test_settings.rds"))
ig_auth(username=settings$dev$username, password=settings$dev$password)
```

```{r load-package, eval=FALSE}
library(Rinstapkg)
ig_auth(username = "MY_USERNAME", password = "MY_PASSWORD") 
```

After logging in with `ig_auth()`, you can check your connectivity by looking at 
the information returned about your timeline (`ig_my_timeline()`), inbox (`ig_my_inbox()`), 
or recent activity (`ig_my_recent_activity()`). It should be information about you!

### Timeline Feed

A simple function to start with is verifying that you can retrieve your timeline as 
it would appear in the Instagramm app or online. This function returns data that 
would appear in the authenticated user's timeline feed. By default, the data is 
returned as a tidy `tbl_df` where each row represents one post from the feed. If 
you prefer to work with a list format, then just specify `return_df=FALSE` as an 
argument.

```{r timeline-feed}
timeline_results <- ig_my_timeline()
timeline_results
```

### Get Followers

With the `ig_get_followers()` function you can retrieve a `tbl_df` of all the users 
that follow a particular user. Just provide the `user_id` of the account whose followers 
you would like to get. **NOTE**: The Instagram APIs use Ids to retrieve information so 
instead of giving the account's username (typically starting with an \@symbol), you 
need to first grab the `user_id` of that account using the username, then supply it 
to the `ig_get_followers()` function. 

```{r get-followers-1}
# Get Justin's Biebers beliebers!
# Side Note: A belieber is a HUGE Justin Bieber fan.
bieber_user_id <- ig_get_user_id("justinbieber")
follower_results <- ig_get_followers(bieber_user_id)
follower_results
```

In the example above you'll notice that we didn't retrieve all 100M+ followers that 
Justin Bieber has. By default the function only returns the top 10 pages of followers, 
but you can set the `max_pages` argument equal to `Inf` to return all of them. Caution: 
This might take awhile!

```{r get-followers-2, eval=FALSE}
# return all 100M+ followers of Justin Bieber
follower_results <- ig_get_followers(bieber_user_id, max_pages = Inf)
```

### Get Following

With the `ig_get_following()` function you can retrieve a `tbl_df` of all the users 
that a particular user is following. For example, Justin Bieber follows ~100 users. Who 
are those lucky few?

```{r get-following}
following_results <- ig_get_following(bieber_user_id)
following_results
```

### Check out the Tests

The **Rinstapkg** package has quite a bit of unit test coverage. These tests are an 
excellent source of examples because they cover most all cases of utilizing the 
package functions, which goes beyond what we have covered here in the "Getting Started" 
vignette. 
